Dominance Regions for Rank Two Cluster Algebras

### 2022-05-08 dominance_regions.tex
Section 6 cleanup

  \begin{theorem}
    \cite{qin}
    \sayDR{Quote Fan's result here.}
  \end{theorem}

@@

  Observe that the last equality can be rewritten as
  \[ \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0) + (\mu_1-\lambda_1) \leq -c\lambda_0 - \frac{b c + \sqrt{b c (b c-4)}}{2 } \lambda_1,\]
  which together with the second to last inequality gives two boundaries for the dominance region $\cP_\lambda$.
  Note then that, under the assumption $\mu_0\leq\lambda_0$, the inequality 
  \[0 \leq \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1)\]
  defining another boundary of $\cP_\lambda$ is more restrictive than the inequality $\lambda_1\leq\mu_1$ bounding $\cS_\lambda$.

@@

  Similarly, the second to last inequality can be rewritten as
  \[ \frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)+(\mu_0-\lambda'_0) \leq -b\lambda'_1-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda'_0,\]
  which together with the last inequality gives two boundaries for the opposite dominance region $\cP'_\lambda$.
  Note then that, under the assumption $\mu_1\leq\lambda'_1$, the inequality
  \[ 0 \leq \frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)+(\mu_0-\lambda'_0) \]
  defining another boundary of $\cP_\lambda$ is more restrictive than the inequality $\lambda'_0\leq\mu_0$ bounding $\cS_\lambda$.
  As above, the minimum value of $\mu_1$ inside $\cP'_\lambda$ occurs when $\mu_0=0$, i.e. either at the point $\big(0, \frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda'_0+\lambda'_1 \big)$
  %\[\big(0, \frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda'_0+\lambda'_1 \big) = \big(0, -\frac{bc-\sqrt{bc(bc-4)}}{2b}(\lambda_0+b\lambda_1)+\lambda_1 \big)\]
  when $0 \leq 2\lambda'_0+b\lambda'_1$ or at the point $-\frac{bc+\sqrt{bc(bc-4)}}{2b} \big(0, \lambda'_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda'_1 \big)$
  %\[-\frac{bc+\sqrt{bc(bc-4)}}{2b} \big(0, \lambda'_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda'_1 \big) = -\frac{bc+\sqrt{bc(bc-4)}}{2b} \big(0, -\frac{bc-2+\sqrt{bc(bc-4)}}{2}(\lambda_0+b\lambda_1)+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1 \big)\]
  when $2\lambda'_0+b\lambda'_1<0$.
  The second point can be rewritten as
  \[\big(0, -\frac{bc+\sqrt{bc(bc-4)}}{2b} \lambda'_0-\frac{bc+\sqrt{bc(bc-4)}}{2b} b\lambda'_1+\lambda'_1 \big)\]
  but, since $b\lambda'_1\le -2\lambda'_0$, the first coordinate is greater than $\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda'_0+\lambda'_1$.
  Then, using $\frac{bc+\sqrt{bc(bc-4}}{2b}<c$ and $\lambda'_0<0$, we see that the minimum value of $\mu_1$ inside $\cP'_\lambda$ satisfies the inequality $\lambda_1=c\lambda'_0+\lambda'_1\le\mu_1$ and so $\cP'_\lambda\subset\cS_\lambda$.

@@

  As we saw above, for any $\bfg$-vector $\mu\in\cP_\lambda$ its opposite $\bfg$-vector $\mu'$ is also contained in $\cS_\lambda$.
  But $\cS_\lambda$ is min-convex and closed under downward scaling, i.e. for any $\mu\in\cS_\lambda$ we have $t\mu\in\cS_\lambda$ for $0\le t\le 1$.
  It follows that $\overline{\cG}_\mu\subset\cS_\lambda$ for any $\mu\in\cP_\lambda$ and so the support of any basis element pointed at $\lambda$ is contained in $\cS_\lambda$.

>>>>

  \begin{theorem}
    \label{th:dominance}
    \cite{qin}
    \sayDR{Quote Fan's result here.}
  \end{theorem}

@@

  Observe that the last equality can be rewritten as
  \[ \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0) + (\mu_1-\lambda_1) \leq -c\lambda_0 - \frac{b c + \sqrt{b c (b c-4)}}{2 } \lambda_1,\]
  which together with the second to last inequality already gives two of the boundaries for the dominance region $\cP_\lambda$.
  Note then that, under the assumption $\mu_0\leq\lambda_0$, the inequality 
  \[0 \leq \frac{b c-\sqrt{b c (b c-4)}}{2 b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1)\]
  defining another boundary of $\cP_\lambda$ is more restrictive than the inequality $\lambda_1\leq\mu_1$ bounding $\cS_\lambda$.

@@

  Similarly, the second to last inequality can be rewritten as
  \[ \frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)+(\mu_0-\lambda'_0) \leq -b\lambda'_1-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda'_0,\]
  which together with the last inequality already gives two of the boundaries for the opposite dominance region $\cP'_\lambda$.
  Note then that, under the assumption $\mu_1\leq\lambda'_1$, the inequality
  \[ 0 \leq \frac{b c-\sqrt{b c (b c-4)}}{2 c}(\mu_1-\lambda'_1)+(\mu_0-\lambda'_0) \]
  defining another boundary of $\cP_\lambda$ is more restrictive than the inequality $\lambda'_0\leq\mu_0$ bounding $\cS_\lambda$.
  As above, the minimum value of $\mu_1$ inside $\cP'_\lambda$ occurs when $\mu_0=0$, i.e. either at the point $\big(0, \frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda'_0+\lambda'_1 \big)$
  %\[\big(0, \frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda'_0+\lambda'_1 \big) = \big(0, -\frac{bc-\sqrt{bc(bc-4)}}{2b}(\lambda_0+b\lambda_1)+\lambda_1 \big)\]
  when $0 \leq 2\lambda'_0+b\lambda'_1$ or at the point $-\frac{bc+\sqrt{bc(bc-4)}}{2b} \big(0, \lambda'_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda'_1 \big)$
  %\[-\frac{bc+\sqrt{bc(bc-4)}}{2b} \big(0, \lambda'_0+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda'_1 \big) = -\frac{bc+\sqrt{bc(bc-4)}}{2b} \big(0, -\frac{bc-2+\sqrt{bc(bc-4)}}{2}(\lambda_0+b\lambda_1)+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_1 \big)\]
  when $2\lambda'_0+b\lambda'_1<0$.
  The second point can be rewritten as
  \[\big(0, -\frac{bc+\sqrt{bc(bc-4)}}{2b} \lambda'_0-\frac{bc+\sqrt{bc(bc-4)}}{2b} b\lambda'_1+\lambda'_1 \big)\]
  but, since $b\lambda'_1\le -2\lambda'_0$, the first coordinate is greater than $\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda'_0+\lambda'_1$.
  Then, using $\frac{bc+\sqrt{bc(bc-4}}{2b}<c$ and $\lambda'_0<0$, we see that the minimum value of $\mu_1$ inside $\cP'_\lambda$ satisfies the inequality $\lambda_1=c\lambda'_0+\lambda'_1\le\mu_1$ and so $\cP'_\lambda\subset\cS_\lambda$.

  To continue, we compare the support for an arbitrary basis element pointed at $\lambda\in\cI$ with the corresponding greedy basis elements with $\bfg$-vectors inside the dominance polygon $\cP_\lambda$.

@@

  As we saw above, for any $\bfg$-vector $\mu\in\cP_\lambda$ its opposite $\bfg$-vector $\mu'$ is also contained in $\cS_\lambda$.
  But $\cS_\lambda$ is min-convex and closed under downward scaling, i.e. for any $\mu\in\cS_\lambda$ we have $t\mu\in\cS_\lambda$ for $0\le t\le 1$.
  It follows that $\overline{\cG}_\mu\subset\cS_\lambda$ for any $\mu\in\cP_\lambda$ and hence, following Theorem~\ref{th:dominance}, the support of any basis element pointed at $\lambda$ is contained in $\cS_\lambda$.
